---
title: "individual2"
author: "Jonathan Kelly"
date: "9/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

```{r}
hist(choco$Rating, xlab='Rating', main='Chocolate Ranking')
```

```{r}
boxplot(choco$Rating, ylab='Rating', main='Chocolate Ranking')
```

How are the ratings distributed? Create both a histogram and a boxplot and describe them. Don’t forget to mention outliers, if there are any.

The ratings are mostly right justified but there a few outliers that ranked very low. There is also a strange hole in the histogram around the 3.1 to 3.2 range.

```{r}
barplot(table(choco$Date), ylab='Rating', xlab='Year', main='Chocolate Ranking depending on Year')
```

How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

The rating start fairly low around 60 in 2006 and slowly increases until it reaches a max at around 270 in 2015 and then begins to decrease again with sharp decreases in 2017 and 2020.
But the sharp decrease in 2020 could be attributed to the fact that they are still getting data for the year.

```{r}
chocoRating <- choco$Rating
chocoPercent <- choco$Cocoa_Percent
plot(chocoRating, chocoPercent)
points(chocoRating, chocoPercent, col='blue', pch=2)
cor(chocoRating, chocoPercent)
```

Do ratings depend on the cacao percentage of a chocolate bar? Create both numerical and graphical summaries, and explain.

There is basically no correlation between cacao percentage and the rating of the chocolate bar, the graph is extremely hard to follow and is very hard to follow.
The correlation is a -.15 which would be a very weak negative correlation. 


