---
title: "team"
author: "Jonathan Kelly and Max Wisnieski"
date: "9/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

## First Analysis

One analysis I wanted to look into was if there was any correlation between ingredients of the chocolate and its rating. I wanted to see if there were any ingredients that were more desirable, and if any were less desirable.

```{r}
rating <- choco$Rating
boxplot(rating~choco$Ingredients, main = "Box Plots of Rating for Ingredients", xlab = "Ingredients", ylab = "Ratings")
ingrating <- choco[,c('Ingredients','Rating')]
ingorder <- ingrating[order(ingrating[,2], decreasing = TRUE),]
top <- head(ingorder, 25)
toptab <- table(top$Ingredients)
barplot(toptab, main = "Ingredients of Top 25 Chocolates", xlab = "Ingredients", ylab = "Frequency")
bot <- tail(ingorder, 25)
bottab <- table(bot$Ingredients)
barplot(bottab, main = "Ingredients of Top 25 Chocolates", xlab = "Ingredients", ylab = "Frequency")
ingredTop <- ingrating[ingrating$Ingredients == '3- B,S,C',]
summary(ingredTop)
ingredTop2 <- ingrating[ingrating$Ingredients == '2- B,S',]
summary(ingredTop2)
ingredBottom <- ingrating[ingrating$Ingredients == '5- B,S,C,V,L',]
summary(ingredBottom)
ingredBottom2 <- ingrating[ingrating$Ingredients == '3- B,S,L',]
summary(ingredBottom2)
```

For my analysis I first looked at box plots for all of the ingredients, then looked at bar charts for the ingredients in the 25 highest and lowest rated chocolates. I then took some of the ingredients that were common on the top and bottom to do some summary statistics.

**Analysis: **From the box plots you can see that there isn't a whole lot of deviation in ratings based on the ingredients. Next, looking at the bar charts it can be seen that '3-B,S,C' is very common in the top 25 rated chocolates, while '5-B,S,C,V,L' is very common in the bottom 25. Finally, looking at the summary statistics we can see that '3-B,S,C' had an average rating of 3.275 and a max rating of 4.0, so it is very desirable to have in chocolate. However, '3-B,S,L' has an average rating of 2.688 and a maximum of 3.25, so it is a poor choice for making chocolate.